---
title: "Great Bay Scallop Search"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
css: styles.css
---

```{r, message = F, warning = F, echo = F}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, echo = F, fig.path = 'figs/')

library(tidyverse)
library(sf)
library(mapview)
library(flexdashboard)
library(extrafont)
library(shiny)
library(colorspace)
library(leaflet)

source('R/funcs.R')

loadfonts(device = 'pdf', quiet = T)
if(Sys.info()[1] == 'Windows')
  loadfonts(device = 'win', quiet = T)

col <- '#00806E'

data(cntdat)
data(hex)
```

2020 {data-navmenu="RESULTS BY YEAR"}
=======================================================================

Column
-------------------------------------

### Hexagons show site locations where volunteers searched for scallops.  Counts for the total number of scallops found at each site are shown by the intensity of the colors, including sites which were searched but no scallops were found.  Sites that were not searched are transparent.  Raw data with missing or incorrect site numbers were omitted.  

```{r, out.width = '100%'}
yr <- 2020
plo_fun(cntdat, yr)
```

Column
-------------------------------------

### 

```{r}
sclbox_fun(cntdat, yr)
```

###

```{r}
btsbox_fun(cntdat, yr)
```

###

```{r}
lcsbox_fun(cntdat, yr)
```

2019 {data-navmenu="RESULTS BY YEAR"}
=======================================================================

Column
-------------------------------------

### Hexagons show site locations where volunteers searched for scallops.  Counts for the total number of scallops found at each site are shown by the intensity of the colors, including sites which were searched but no scallops were found.  Sites that were not searched are transparent.  Raw data with missing or incorrect site numbers were omitted.  

```{r, out.width = '100%'}
yr <- 2019
plo_fun(cntdat, yr)
```

Column
-------------------------------------

### 

```{r}
sclbox_fun(cntdat, yr)
```

###

```{r}
btsbox_fun(cntdat, yr)
```

###

```{r}
lcsbox_fun(cntdat, yr)
```

2017 {data-navmenu="RESULTS BY YEAR"}
=======================================================================

Column
-------------------------------------

### Hexagons show site locations where volunteers searched for scallops.  Counts for the total number of scallops found at each site are shown by the intensity of the colors, including sites which were searched but no scallops were found.  Sites that were not searched are transparent.  Raw data with missing or incorrect site numbers were omitted.  

```{r, out.width = '100%'}
yr <- 2017
plo_fun(cntdat, yr)
```

Column
-------------------------------------

### 

```{r}
sclbox_fun(cntdat, yr)
```

###

```{r}
btsbox_fun(cntdat, yr)
```

###

```{r}
lcsbox_fun(cntdat, yr)
```

2015 {data-navmenu="RESULTS BY YEAR"}
=======================================================================

Column
-------------------------------------

### Hexagons show site locations where volunteers searched for scallops.  Counts for the total number of scallops found at each site are shown by the intensity of the colors, including sites which were searched but no scallops were found.  Sites that were not searched are transparent.  Raw data with missing or incorrect site numbers were omitted.  

```{r, out.width = '100%'}
yr <- 2015
plo_fun(cntdat, yr)
```

Column
-------------------------------------

### 

```{r}
sclbox_fun(cntdat, yr)
```

###

```{r}
btsbox_fun(cntdat, yr)
```

###

```{r}
lcsbox_fun(cntdat, yr)
```

2014 {data-navmenu="RESULTS BY YEAR"}
=======================================================================

Column
-------------------------------------

### Hexagons show site locations where volunteers searched for scallops.  Counts for the total number of scallops found at each site are shown by the intensity of the colors, including sites which were searched but no scallops were found.  Sites that were not searched are transparent.  Raw data with missing or incorrect site numbers were omitted.  

```{r, out.width = '100%'}
yr <- 2014
plo_fun(cntdat, yr)
```

Column
-------------------------------------

### 

```{r}
sclbox_fun(cntdat, yr)
```

###

```{r}
btsbox_fun(cntdat, yr)
```

###

```{r}
lcsbox_fun(cntdat, yr)
```

2011 {data-navmenu="RESULTS BY YEAR"}
=======================================================================

Column
-------------------------------------

### Hexagons show site locations where volunteers searched for scallops.  Counts for the total number of scallops found at each site are shown by the intensity of the colors, including sites which were searched but no scallops were found.  Sites that were not searched are transparent.  Raw data with missing or incorrect site numbers were omitted.  

```{r, out.width = '100%'}
yr <- 2011
plo_fun(cntdat, yr)
```

Column
-------------------------------------

### 

```{r}
sclbox_fun(cntdat, yr)
```

###

```{r}
btsbox_fun(cntdat, yr)
```

###

```{r}
lcsbox_fun(cntdat, yr)
```

2010 {data-navmenu="RESULTS BY YEAR"}
=======================================================================

Column
-------------------------------------

### Hexagons show site locations where volunteers searched for scallops.  Counts for the total number of scallops found at each site are shown by the intensity of the colors, including sites which were searched but no scallops were found.  Sites that were not searched are transparent.  Raw data with missing or incorrect site numbers were omitted.  

```{r, out.width = '100%'}
yr <- 2010
plo_fun(cntdat, yr)
```

Column
-------------------------------------

### 

```{r}
sclbox_fun(cntdat, yr)
```

###

```{r}
btsbox_fun(cntdat, yr)
```

###

```{r}
lcsbox_fun(cntdat, yr)
```

2009 {data-navmenu="RESULTS BY YEAR"}
=======================================================================

Column
-------------------------------------

### Hexagons show site locations where volunteers searched for scallops.  Counts for the total number of scallops found at each site are shown by the intensity of the colors, including sites which were searched but no scallops were found.  Sites that were not searched are transparent.  Raw data with missing or incorrect site numbers were omitted.  

```{r, out.width = '100%'}
yr <- 2009
plo_fun(cntdat, yr)
```

Column
-------------------------------------

### 

```{r}
sclbox_fun(cntdat, yr)
```

###

```{r}
btsbox_fun(cntdat, yr)
```

###

```{r}
lcsbox_fun(cntdat, yr)
```

2008 {data-navmenu="RESULTS BY YEAR"}
=======================================================================

Column
-------------------------------------

### Hexagons show site locations where volunteers searched for scallops.  Counts for the total number of scallops found at each site are shown by the intensity of the colors, including sites which were searched but no scallops were found.  Sites that were not searched are transparent.  Raw data with missing or incorrect site numbers were omitted.  

```{r, out.width = '100%'}
yr <- 2008
plo_fun(cntdat, yr)
```

Column
-------------------------------------

### 

```{r}
sclbox_fun(cntdat, yr)
```

###

```{r}
btsbox_fun(cntdat, yr)
```

###

```{r}
lcsbox_fun(cntdat, yr)
```

2007 {data-navmenu="RESULTS BY YEAR"}
=======================================================================

Column
-------------------------------------

### Hexagons show site locations where volunteers searched for scallops.  Counts for the total number of scallops found at each site are shown by the intensity of the colors, including sites which were searched but no scallops were found.  Sites that were not searched are transparent.  Raw data with missing or incorrect site numbers were omitted.  

```{r, out.width = '100%'}
yr <- 2007
plo_fun(cntdat, yr)
```

Column
-------------------------------------

### 

```{r}
sclbox_fun(cntdat, yr)
```

###

```{r}
btsbox_fun(cntdat, yr)
```

###

```{r}
lcsbox_fun(cntdat, yr)
```


